---
title: "Project 1 - Mickey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
format:
  html:
    embed-resources: true
    code-overflow: wrap
editor: visual
---

## Our Team

Fill the vector `our_team` with the full names (First Last) of each team member. Although this task is worth no points, failing to complete this task will result in a one-point deduction.

```{r}
our_team = c('Arnold Jiang', 'John Woo', 'Tong Dai', 'Willow Yang')
our_team
```

------------------------------------------------------------------------

## Introduction

The Walt Disney Company is an American multinational mass media and entertainment conglomerate. Its brand, often represented by their cartoon character Mickey Mouse, is recognized in every corner of the world.

In this project, we will focus on data gathered from three components of this business empire:

A.  Walt Disney Movies
B.  Disney+ Streaming
C.  Company Financials

At the conclusion of each section, a written summary (5-10 sentences) of your work is required. The summaries should include:

-   insights from your exploratory data analysis
-   patterns recognized through your presented charts
-   pros and cons of the methods used to complete the section

All charts must be labeled and styled beyond the default settings to display a clear and helpful narrative.

The project will be graded on a basis of 100 maximum points.

------------------------------------------------------------------------

## The Necessary Packages

Run this entire code chunk BEFORE proceeding to ensure that all subsequent code are recognized and executable.

```{r packages}
#| message: false
library(tidyverse)
library(highcharter)
library(gt)
```

------------------------------------------------------------------------

## A. Disney Movies \[*40 pts total*\]

The Walt Disney Studios is a major force in the entertainment industry. It is one of the "Big Five" studios (Universal, Paramount, Warner Bros, and Sony Pictures being the others). In this section, you will explore data related to this important arm of the Disney empire.

#### A0. Data

The `dis_movies` dataset contains a collection of movies produced by Walt Disney Studios and affiliates since 1937 ([Source](https://www.the-numbers.com/box-office-records/worldwide/all-movies/theatrical-distributors/walt-disney)). Run the following code chunk to import this dataset into your environment.

```{r a0}
#| message: false

dis_movies = read_csv(file = 'https://www.dropbox.com/scl/fi/q5tot6ylmqvzyv1ve73jk/dis_movies.csv?rlkey=i6nrb7htoimm025kxxitegue9&st=ha0pbdxj&raw=1')
```

Data Dictionary

-   yor: year of release of movie
-   movie: title of the movie
-   box_dom: the lifetime domestic (US) box office revenue (\$US) for the movie
-   box_int: the lifetime international (non-US) box office revenue (\$US) for the movie

All box office figures are unadjusted for inflation.

#### A1. EDA \[*24 pts total*\]

##### A1a. Top 50 Movies \[*8 pts*\]

-   Create and display (using `gt`) a data frame (`dis_25`) that will hold all the columns from `dis_movies` for the top 25 movies based on worldwide box office revenue.

```{r a1a}

dis_25 <- dis_movies %>%
    mutate(
        total_worldwide = box_dom + box_int,
        box_dom =round(box_dom / 1e6, digits = 2),
        box_int = round(box_int / 1e6, digits = 2),
        total_worldwide = round(total_worldwide / 1e6, digits = 2)
    ) %>%
    slice_max(n = 25, total_worldwide) %>%
    gt() %>% 
    tab_header(
        title = "Top 25 movies based on worldwide box office revenue"
    ) %>%
    cols_label(
        yor = html("Year of Release"),
        movie = html("Movie Name"),
        box_dom = html("Domestic Revenue (Million USD)"),
        box_int = html("International Revenue (Million USD)"),
        total_worldwide = html("Worldwide Revenue (Million USD)")
    ) %>%
    opt_stylize(style = 6, color = "cyan")

dis_25
```

##### A1b. Boost from Afar \[*8 pts*\]

-   Identify, by filtering `dis_movies`, the 100 movies that have the greatest portion of their worldwide box office revenue from international sales. Display only the top 10 (based on the international percentage) of these movies using `gt`.

```{r a1b}

dis_100 <- dis_movies %>%
    mutate(
        total_worldwide = box_dom + box_int,
        percentage = box_int / total_worldwide * 100,
        
    ) %>%
  arrange(desc(percentage)) %>%
  filter(row_number() <= 100)

dis_10 <- dis_100 %>%
    top_n(10, percentage) %>%
    select(yor, movie, box_dom, box_int) %>%
    gt() %>% 
    tab_header(
        title = "Top 10 Movies with the Greatest Portion of Their Worldwide Box Office Revenue From International Sales"
    ) %>%
    cols_label(
        yor = html("Year of Release"),
        movie = html("Movie Name"),
        box_dom = html("Domestic Revenue"),
        box_int = html("International Revenue")
    ) %>%
    opt_stylize(style = 6, color = "red")

dis_10
```

##### A1c. Adjusted Box Office \[*8 pts*\]

-   Create a new column in `dis_movies` called `box_dom_adj` which will hold the domestic box office revenue for each movie adjusted for inflation.

-   Assume an annual inflation rate of 0.03.

-   The formula to approximate adjusted box office is:

$$
box\_dom\_adj=box\_dom\cdot (1+i)^{\frac{2024-yor}{1.5}}
$$

```{r a1c}

dis_movies <- dis_movies %>%
    mutate(
        box_dom_adj = box_dom * (1 + 0.03)^{(2024-yor)/(1.5)}
    ) 

dis_movies %>%
    gt() %>% 
    tab_header(
        title = "Disney Movies with Domestic Box Office Revenue Adjusted for Inflation"
    ) %>%
    cols_label(
        yor = html("Year of Release"),
        movie = html("Movie Name"),
        box_dom = html("Domestic Revenue"),
        box_int = html("International Revenue"),
        box_dom_adj = html("Domestic Revenue (Adjusted)")
    ) %>%
    opt_stylize(style = 6, color = "blue")

```

#### A2. Charts \[*16 pts total*\]

test pushing

##### A2a. Box Office Distribution \[*8 pts*\]

-   Generate a scatterplot (in `ggplot2`) of the inflation-adjusted domestic box office revenue of all movies released in the 2000s (2000-2009).
    -   x = yor

    -   y = box_dom_adj

```{r a2a}
two_thousands_movies <- dis_movies |>
  filter(yor >= 2000 & yor <= 2009) 

min_box = min(two_thousands_movies$box_dom_adj)
max_box = max(two_thousands_movies$box_dom_adj)

two_thousands_movies |> 
  ggplot(aes(x = yor, y = box_dom_adj, color = box_dom_adj)) +
  geom_point() +
  labs(title = "Inflation-Adjusted Domestic Revenue of Movies Released in 2000-2009",
       x = 'Year of Release', 
       y = 'Domestic Box Office (Adjusted)') + 
  lims(y = c(min_box, max_box)) + 
  scale_x_continuous(breaks = seq(2000, 2009, 1)) +
  scale_color_gradient(low = 'lightblue', high = 'blue') +
  theme(
    plot.title = element_text(color = 'purple'),
    axis.title.x = element_text(color = 'purple'),
    axis.title.y = element_text(color = 'purple'),
  )
```

##### A2b. Five-Year Trend \[*8 pts*\]

-   Choose an appropriate chart (in `highcharter`) to show the trends in box office revenue for any five-year span of your choosing.

```{r a2b}

filtered_movies_2 <- dis_movies |>
  filter(yor >= 2019 & yor <= 2023)

box_int_by_year <- filtered_movies_2 |>
  group_by(yor) |>
  summarise(year_box_int = sum(box_int))

box_int_by_year |> 
  hchart(
    hcaes(
      x = yor, 
      y = year_box_int
    ), 
    type = "column", 
    name = "Box Office Revenue of Disney Movies"
  ) |>
  hc_title(text = "Trends in International Revenue of Disney Movies from 2019-2023") |>
  hc_xAxis(title = list(text = "Year Of Release")) |>
  hc_yAxis(title = list(text = "International Revenue (Billions)")) 

# We chose 2019 to 2023 because we wanted to see what impact Covid 
# had on international Revenue of Disney Movies
paste("We chose 2019 to 2023 because we wanted to see what 
  impact Covid had on international Revenue of Disney Movies")
```

#### A3. Summary \[*3 pts*\]

Write a concluding paragraph on your observations during the completion of this section. Contain all your words within the blockquote below by replacing the word 'Summary' with your text.

> We observed that none of the top 10 movies with the greatest portion of their worldwide revenue from international sales are included in the top 25 movies with highest worldwide box office revenue. This suggests that the films with the highest overall (worldwide) revenue tend to do so primarily from domestic sales, rather than relying heavily on international success. In addition, we noticed that among Disney movies released between 2019 and 2023, 2019 recorded the highest international box office revenues, while 2020 had the lowest. However, from 2020 to 2023, there is an upward trend in the international box office revenues. This upward trend from 2020 to 2023 in the international box office revenues among Disney movies reflects the gradual recovery from the COVID-19 pandemic.

------------------------------------------------------------------------

## B. Disney+ \[*30 pts total*\]

Since its launch in November 2019, Disney+ streaming service has seen consistent growth in its subscriber base. With access to every Disney movie and TV show, this has been a favorite among Disney fans. In this section, you will explore data related to this growing service catering to users of all ages.

#### B0. Data

The `dis_plus` dataset contains a quarterly report of Disney+ subscribers as well as the corresponding counts for the king of Video On Demand service - Netflix ([Source](https://www.statista.com/statistics/1095372/disney-plus-number-of-subscribers-us/)). Run the following code chunk to import this dataset into your environment.

```{r b0}
#| message: false

dis_plus = read_csv(file = 'https://www.dropbox.com/scl/fi/5kt0kzhnpop3ub9qavnzm/dis_plus.csv?rlkey=b3eqvyhthfpgxxd7sdzzru00y&st=aw0bree0&raw=1')
```

Data Dictionary

-   year: year of subscriber measurement
-   qtr: quarter of subscriber measurement
-   dis_subs: the number of total subscribers (in millions) to Disney+ as of the end of the given qtr & year
-   nflx_subs: the number of total subscribers (in millions) to Netflix as of the end of the given qtr & year

#### B1. Disney+ \[*15 pts total*\]

##### B1a. Qtr-over-Qtr Growth \[*9 pts*\]

-   For Disney+ subscribers, evaluate the quarter-over-quarter growth rate for each pair of consecutive quarters.
-   Express the growth rates as decimals rounded to 3 dp.
-   In a comment, state which quarter & year experienced the greatest rate of growth.

```{r b1a}

dis_plus <- dis_plus |>
  mutate(qtr_over_qtr_growth = round((dis_subs - lag(dis_subs)) / dis_subs * 100, 3)) |>
  mutate(qtr_over_qtr_growth = ifelse(is.na(qtr_over_qtr_growth), 0, qtr_over_qtr_growth))

greatest_growth_year <- dis_plus |>
  filter(qtr_over_qtr_growth == max(qtr_over_qtr_growth, na.rm = T)) |>
  pull(year)

greatest_growth_qtr <- dis_plus |>
  filter(qtr_over_qtr_growth == max(qtr_over_qtr_growth, na.rm = T)) |>
  pull(qtr)

# the greatest rate of growth happened during year 2020 qtr 3.
paste("The greatest rate of growth happened during year", greatest_growth_year, "qtr", greatest_growth_qtr) 

dis_plus |> 
  gt() |>
  tab_header(
      title = "Quarter-Over-Quarter Growth Rate for Each Pair of Consecutive Quarter"
  ) |> 
  cols_label(
      year = html("Year"),
      qtr = html("Quarter"),
      dis_subs = html("Disney Subscribers (in Millions)"),
      nflx_subs = html("Netflix Subscribers (in Millions)"),
      qtr_over_qtr_growth = html("Quarter-Over-Quarter Growth Rate")
  ) |>
  opt_stylize(style = 6, color = "green")



```

##### B1b. Annual Totals \[*6 pts*\]

-   For each year of data, provide annualized summaries for Disney+ subscribers:
    -   average quarterly subscribers

    -   highest quarterly subscribers

    -   lowest quarterly subscribers

    -   range of quarterly subscribers

```{r b1b}

annualized_sum <- dis_plus |>
  group_by(year) |>
  summarise(avg_qtr_subs = sum(dis_subs) / 4,
            highest_qtr_subs = max(dis_subs),
            lowest_qtr_subs = min(dis_subs),
            range_qtr_subs = highest_qtr_subs - lowest_qtr_subs,
            )

annualized_sum |>
  gt() |>
  tab_header(
      title = "Annualized Summaries for Disney+ Subscribers (in Millions)"
  ) |> 
  cols_label(
      year = html("Year"),
      avg_qtr_subs = html("Average Quarterly Subscribers"),
      highest_qtr_subs = html("Highest Quarterly Subscribers"),
      lowest_qtr_subs = html("Lowest Quarterly Subscribers"),
      range_qtr_subs = html("Range of Quarterly Subscribers"), 
  ) |>
  opt_stylize(style = 6, color = "blue")
```

#### B2. Comparisons \[*15 pts total*\]

##### B2a. Stacking Up Against Netflix \[*15 pts*\]

-   Generate a combination plot with the subscriber counts for both Disney+ and Netflix as a function of qtr & year.
-   Use either `ggplot2` or `highcharter`.
-   Present both series as lines, being sure to style all parts of the chart to present a compelling storyline.

```{r b2a}

dis_plus <- dis_plus |> 
  mutate(year_qtr = paste0("Q", qtr, "-", year)) 

hchart(
  object = dis_plus,
  mapping = hcaes(x = year_qtr, y = dis_subs),
  type = 'line',
  color = 'orange',
  yAxis = 0,
  name = "Disney+ Subscribers (Millions)"
) |> 
  hc_add_series( 
    data = dis_plus,
    mapping = hcaes(x = year_qtr, y = nflx_subs),
    type = 'line',
    color = 'red',
    yAxis = 1,
    name = "Subscriber Counts for Disney+ and Netflix"
  ) |> 
  hc_yAxis_multiples(
    list(title = list(text = 'Disney+ Subscribers (in Millions)', style = list(color = "orange"))),
    list(opposite = TRUE, title = list(text = 'Netflix Subscribers (in Millions)', style = list(color = "red")))
  ) |>
  hc_title(text = "Subscriber Counts for Disney+ and Netflix", align = "center") |>
  # hc_xAxis(title = list(text = "Year and Quarter")) 
  hc_xAxis(
    title = list(text = "Year and Quarter"),
    categories = unique(dis_plus$year_qtr),
    tickInterval = 1
  )

```

#### B3. Summary \[*3 pts*\]

Write a concluding paragraph on your observations during the completion of this section. Contain all your words within the blockquote below by replacing the word 'Summary' with your text.

> We observe that Disney+ has a high growth rate over 20% in the beginning from 2020 quarter 1 to 2021 quarter 1, but gradually has steady single digit percent of growth from 2021 quarter 2 to 2022 quarter 4. From 2023 quarter 1 to 2024 quarter 4, the growth rate of Disney+ subscribers is generally minimal or decreasing. Meanwhile, Netflix, the king of Video On Demand service, is consistently having positive growth rate other than 2022 quarter 2. Annually, lowest bound of quarterly Disney+ subscribers is increasing, and range of quarterly subscribers is decreasing, but quarterly highest Disney+ subscribers peaked in 2022, then it decreased. We also see that in 2020 quarter 1 Netflix has more subscribers than Disney+, but in 2021 quarter 3 and 2021 quarter 4, and from 2022 Quarter 3 to 2023 Quarter 2, Disney+ surpassed Netflix in quarterly subscribers, and throughout 2020 Quarter 1 to 2023 Quarter 2, the quarterly subscribers is similar between Netflix and Disney+, but starting from 2023 Quarter 3, the amount of quarterly Disney+ subscribers plateaus, while Netflix's quarterly subscribers is still growing.

------------------------------------------------------------------------

## C. Company Financials \[*30 pts total*\]

The Walt Disney Company is a publicly-traded company (NYSE: DIS) that has been a fixture in the Dow Jones Industrial Average since 1991. In this section, you will explore data related to daily share prices of this company's common stock.

#### C0. Data

The `dis_stock` dataset contains daily trading data for DIS stock for the 2500 trading days prior to 2/8/2025 ([Source](https://finance.yahoo.com/quote/DIS/history/)). Run the following code chunk to import this dataset into your environment.

```{r}
#| message: false

dis_stock = read_csv(file = 'https://www.dropbox.com/scl/fi/x25yj3rp81dn1tipguqk5/dis_stock.csv?rlkey=6j7gkdei81aipn0kem0i34tit&st=rps4871p&raw=1')
```

Data Dictionary

-   date: date of trading day
-   open: the share price at the opening bell
-   high: the intra-day highest share price
-   low: the intra-day lowest share price
-   close: the share price at the closing bell
-   volume: the number of shares traded during the trading day
-   spx: the S&P 500 Index value at the close
-   shrsout: the number of shares (in billions) outstanding of DIS common stock

#### C1. Stock Performance \[*14 pts total*\]

##### C1a. Daily Activity\[*8 pts*\]

-   For all the trading days in `dis_stock`, filter the days such that you retain only the days on which there was at least a 5% gain or loss

```{r c1a}
filtered_dis_stocks <- dis_stock |>
  mutate(percentage = ((close - open) / open) * 100 ) |>
  filter(percentage >= 5 | percentage <= -5)

filtered_dis_stocks |>
  gt() |>
  tab_header(
      title = "Trading Days of DIS Stocks with at least 5% Gain or Loss"
  ) |>
  cols_label(
      date = html("Date"),
      open = html("Open"),
      high = html("High"),
      low = html("Low"),
      close = html("Close"),
      volume = html("Volume"),
      spx = html("SPX"),
      shrsout = html("Outstanding Shares"),
      percentage = html("Chang Over 5%")
  ) |> 
  opt_stylize(style = 6, color = "pink")

```

##### C1b. Market Cap \[*7 pts*\]

-   On which date, was the market capitalization of DIS at its peak?
-   On which month, was the greatest movement (+ or -) of market cap compared to the prior month?
-   The formula for market cap is:

$$
market cap=share price \cdot shares outstanding
$$

-   Use `close` as the share price for each trading day.

```{r c1b}

dis_stock_with_market_cap <-  dis_stock |>
  mutate(market_cap = close * shrsout,
         date_movement = abs(market_cap - lag(market_cap))) 

dis_stock_with_market_cap <- dis_stock_with_market_cap |>
  mutate(date_movement = ifelse(is.na(date_movement), 0, date_movement))

peak_market_cap_date = dis_stock_with_market_cap |>
  filter(market_cap == max(market_cap)) |>
  pull(date)

# the market capitalization of DIS was at its peak on 2021-03-08
paste("The market capitalization of DIS was at its peak on", peak_market_cap_date)

greatest_monthly_movement <- dis_stock_with_market_cap |> 
  filter(date_movement == max(date_movement)) |>
  pull(date)

# the greatest movement of market cap happened in Decemeber of 2020, specifically on 2020-12-10
paste("The greatest movement of market cap happened in Decemeber of 2020, specifically on", greatest_monthly_movement)

```

#### C2. Financial Analysis \[*13 pts total*\]

##### C2a. DIS vs SPX \[*6 pts*\]

-   With 1/2/2021 as the start date, generate a combo chart that will show the growth of \$1 invested in DIS and separately in the S&P 500 Index.
-   Use 12/31/2024 as the end date.
-   Use `ggplot2` for this chart.

```{r c2a}

stock <- dis_stock %>%
  filter(date >= as.Date("2021-01-02") & date <= as.Date("2024-12-31")) %>%
  mutate(
    dis_growth = close / first(close),
    spx_growth = spx / first(spx)
  ) %>%
  select(date, dis_growth, spx_growth)

plot <- stock %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = dis_growth, color = "DIS"), linewidth = 1) +
  geom_line(aes(y = spx_growth, color = "S&P 500"), linewidth = 1) +
  scale_color_manual(values = c("DIS" = "blue", "S&P 500" = "red")) +
  scale_x_date(date_breaks = "3 months", date_labels = "%Y-%m") +
  scale_y_continuous(breaks = seq(0, 2, by = 0.1)) +
  labs(
    title = "Growth of $1 Investment (2021-2024)",
    x = "Date",
    y = "Value of Investment ($)",
    color = "Investment"
  ) +
  theme_classic()

plot
```

##### C2b. OHLC \[*7 pts*\]

-   Using `highcharter`, generate a chart showing the intra-day prices (open, high, low, close) for each trading day in 2024.

```{r c2b}



```

### C3. Summary \[*3 pts*\]

Write a concluding paragraph on your observations during the completion of this section. Contain all your words within the blockquote below by replacing the word 'Summary' with your text.

> Summary

------------------------------------------------------------------------

## Z. Wrap Up

When you are ready to submit your project, follow these steps:

1.  Click the `Render` button to compile this document. An HTML file will be created in the folder containing this QMD file.

2.  While the HTML file is opened in a browser (e.g. Chrome, Safari), print it to a PDF file. Do not choose the 'Export as PDF' option on Safari. This will create one giant page in the PDF, making it impossible to grade. Your final PDF must be separated into individual letter-sized pages before submitting.

3.  Submit the PDF file to **Gradescope** (not to Canvas). Only one person per team needs to submit. Any confusion with multiple entries per team will result in point deductions in the final grade.